Deep Learning for 3D Brain Activity Scans

### 2019-12-02 paper/submission.tex
Warm start results look good

%-------------------------------------------------------------------------
\begin{abstract}
   Abstract placeholder
\end{abstract}

@@

% ----------------------------------------------------------------------
% PROBLEM STATEMENT
% ----------------------------------------------------------------------
\section{Problem Statement}\label{sec:problem-statement}
The dataset to be used is a set of neuro-imaging scans from a cohort of 30 healthy, young women in the
Netherlands circa 2013 who were presented with various grids of images featuring
either neutral entities, (e.g.\ office chairs, windows, jackets) or foods~\cite{smeets2013allured}.
The foods were specifically types of calorically dense, tempting foods, which the individuals viewing would likely
have formed restraint with given their success in maintaining healthy body mass indices.
The experiment was meant to highlight brain structures roles in anticipated rewards from consuming delicious foods,
balanced against the hypothesized activation of restraints.
In neuro-imaging, this task is known as passive image viewing.

@@

>>>>

%-------------------------------------------------------------------------
\begin{abstract}
   Abstract placeholder (sub 300 words)
\end{abstract}

@@

% ----------------------------------------------------------------------
% PROBLEM STATEMENT
% ----------------------------------------------------------------------
\section{Problem Statement}\label{sec:problem-statement}

(BACKGROUND / RELATED)

The dataset to be used is a set of neuro-imaging scans from a cohort of 30 healthy, young women in the
Netherlands circa 2013 who were presented with various grids of images featuring
either neutral entities, (e.g.\ office chairs, windows, jackets) or foods~\cite{smeets2013allured}.
The foods were specifically types of calorically dense, tempting foods, which the individuals viewing would likely
have formed restraint with given their success in maintaining healthy body mass indices.
The experiment was meant to highlight brain structures roles in anticipated rewards from consuming delicious foods,
balanced against the hypothesized activation of restraints.
In neuro-imaging, this task is known as passive image viewing.

@@

PUT BRAIN SCANS IN SUPPLEMENTARY?

abstract > intro > background > related
methods/approach > results > discussion > references
6 pages? 7 maybe at most

gradual warm-start improvements?
variations on models? meh

unsupervised segmentation - little hard

surprisingly bad results on warm starting expansion to new subjects - old same subjects takes a little while to stabilize
but it gets back to 83% without much fuss, probably LR is a little high to start with and the decay helps a lot.
bounces down for a while, bounces up for a while. breaking 90% which is very cool, might mean warm start has best potential

WORK ON GETTING PARAM NUMBERS AND
DIFFERENT METRICS (AUC PLEASE, F1 PLEASE)
2d is enough

Submit your final submission through OpenReview. You will submit a single pdf file:
A pdf file of your final report

(OPTIONAL) supplementary can be concatenated at the end of the final report
Report. The following is a suggested structure for the report:
Title, Author(s)

Abstract: It should not be more than 300 words

Introduction: this section introduces your problem, and the overall plan for approaching your problem
Background/Related Work: This section discusses relevant literature for your project
Approach: This section details the framework of your project. Be specific, which means you might want to include equations, figures, plots, etc
Experiment: This section begins with what kind of experiments you're doing, what kind of dataset(s) you're using, and what is the way you measure or evaluate your results. It then shows in details the results of your experiments. By details, we mean both quantitative evaluations (show numbers, figures, tables, etc) as well as qualitative results (show images, example results, etc).
Conclusion: What have you learned? Suggest future ideas.
References: This is absolutely necessary.
Supplementary Material is not counted toward your 6-8 page limit. It is optional and is supposed to contain less important results/experiments/etc not critical for understanding the main report.

try different architectures - more depth?
see if we can break 85% to 90%, talk about potential data mislabeling frustration as a barrier to higher results possibly

you are expected to show substantially more experiments and results with NN-related methods
( :(  lame)

~\cite{he2016deep} resnet
~\cite{tran2018closer} 3d/time resnet
~\cite{hara3dcnns} 3d cnn pt1?
